{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-29 Paper/main.tex
Drafting simulation results

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset. This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots. These smooth curves are then centered, before performing \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$ Finally, we obtain the generated curves $NIR_{sim}$

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the methods with differing true coefficient functions:

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used 10 fold cross-validation. The simulation was done with R (version...). In total we conducted out 2500 repetitions for each set of simulations. {\color{green} Information about version and link to repo / package in footnote??}

	\subsection{Results}
	DESCRIBE RESULTS

>>>>

	\subsection{Generating Similar Curves}
	To avoid small sample problems, we generated 200 similar curves from the gasoline dataset. This is motivated by \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. First, the initial curves are expressed in terms of a generated bspline basis which is created using 50 knots. These smooth curves are then centered, before applying the \hyperlink{KL}{Karhunen-Lo\'{e}ve Expansion}. It is assumed that the scores follow a normal distribution, thus, the new realizations for the scores are drwan from a multivariate normal $\tilde{\xi} = \left(\tilde{\xi}_{1},\: \dots \:, \tilde{\xi}_{J}\right)' \sim \mathcal{N}(0_J, \; diag(\hat{\lambda}_1,\: \dots\:, \hat{\lambda}_J))$. Finally, we obtain the generated curves $NIR_{sim}$

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, are created that differ in their smoothness, to compare the introduced methods with differing true coefficient functions:

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used 10 fold cross-validation. The simulation was done with R (version...). In total, 5000 repetitions were done for each set of simulations.

	\subsection{Results}
	{\color{green}DESCRIBE RESULTS: make paragraph for each setup? so 6 paragraphs? Like this: }

	\subsubsection{Basis Expansion Regression}
	This follows from the \hyperref[basis_exp_transf]{Basis Expansion Transformation}, in which we transform the observed functions to perform regression of a scalar on a countable sequence of regressors, tractable with typical multivariate regression theory. 
	\paragraph{Monomial Basis}
	\paragraph{Bspline Basis}
	\paragraph{Fourier Basis}
